A Survey of Fuzzing and New Technique for Dynamic Analysis

### 2014-03-11 docs/paper/fsuthesis/thesis-template/paper.tex
started on pin

\section{TODO Intel PIN}

@@

Several valuable techniques to improve fuzzers' code coverage have evolved over the years. Two, in particular, inspire this work directly: Dynamic Taint Analysis and Symbolic Execution. Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing. Symbolic execution improves code coverage by first running a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of SMT solver [CITE] to solve for what value the element should have under certain conditions. Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims for reasonable runtimes while maintaining good code coverage. These each come with their own drawbacks, a primary one of which is the lack of automated instrumentation. Historically, any amount of symbolic execution required a programmer to directly instrument source code, leading much current research to focus on automating as much as possible.

>>>>

\section{Intel PIN}

Heavyweight analysis techniques, like symbolic execution or dynamic taint analysis, which operate over an entire instruction set, must account for the idiosyncracies and diverse operations supported by the architecture. By leveraging a pre-existing framework like Intel Pin [M], new software can abstract away from architecture specific details like x86 variable length instructions and avoid re-inventing the wheel.

Pin, developed by Intel Corporation and the University of Colorado, performs dynamic binary instrumentation on x86, Itanium, and ARM architectures. Pin takes an arbitrary binary to be instrumented and an user-developed dynamically linked library, and instruments the binary at runtime by inserted user defined routines or changes into the application's code.

Pin's architecture is two-fold: consisting of a virtual machine for compiling and executing code, and a cache for previously executed

instrumentation is accomplished with Unix ptrace, similar to debuggers

TODO finish pin stuff

@@

Several valuable techniques for improving fuzzers' code coverage have evolved over the years. Two, in particular, inspire this work directly: Dynamic Taint Analysis and Symbolic Execution. Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing. Symbolic execution improves code coverage by first running a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of SMT solver [CITE] to solve for what value the element should have under certain conditions. Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims for reasonable runtimes while maintaining good code coverage. These each come with their own drawbacks, a primary one of which is the lack of automated instrumentation. Historically, any amount of symbolic execution required a programmer to directly instrument source code, leading much current research to focus on automating as much as possible.
